Appendix: Why the complement of AUC isn't a casewise CV criterion

### 2023-12-31 scratch/notes_georges/AUC_not_casewise-edited-1.Rmd
fix typo in AUC appendix

We can test whether equation (\ref{eq:lin}) has a solution for any given $n_v$ by trying to solve it as a least-squares problem, considering whether the residuals of the associated linear model are all 0, using the "design matrix" $[\mathbf{U} -\mathbf{Y}, \mathbf{Y}]$ to predict the "outcome"
$\mathrm{AUC}(\mathbf{\widehat{Y}},\mathbf{Y})_{(2n_v \times 1)}$:

>>>>

We can test whether equation (\ref{eq:lin}) has a solution for any given $n_v$ by trying to solve it as a least-squares problem, considering whether the residuals of the associated linear model are all 0, using the "design matrix" $[\mathbf{U} -\mathbf{Y}, \mathbf{Y}]$ to predict the "outcome"
$\mathrm{AUC}(\mathbf{\widehat{Y}},\mathbf{Y})_{(2^{n_v} \times 1)}$:
